{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-07 wacv_for_review.tex
Revised the draft.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and on executable code. To develop a single,
target tracking system in high accuracy and run-time performance, we
propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF. In particular, we developed a committee of KCFs to
specifically address the scale-change and dynamic maneuver of the
target over frames. To guarantee a high-speed, run-time performance, we
deploy each of KCFs in turn. For a smooth transition between
individual KCFs' executions, we developed a Bayes filter. Experimental
results showed that the performance of ours are, on average, 70.10\%
for precision at 20 pixels, 53.00\% for success rate for OTB100 data,
and 54.50\% and 40.2\% for UAV123 data. These results showed that our
method is better than existing ones over 5\% on precision on 20 pixels
and 10-20\% on AUC on average. Moreover our implementation ran at 340
fps for OTB100 and at 416 fps for UAV123 data that is faster than DCF
(292 fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a lightweight or an array of monocular cameras. For
example, instead of just flying to record a video based on manual
commands, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

In this paper, we propose a single-target tracking algorithm, with no
offline training, aiming at running on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-450$ fps so that it could run, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would be very hard to compare an Intel
  or AMD processor running on a desktop or a laptop with that, e.g.,
  ARM, of a single-board, embedded system in terms of run-time
  performance of a computer vision algorithm. This is primarily due to
  the difference in their architectures. To derive this number, we
  assume that there is roughly, at least, an 1/10th scale down of
  computational resources from a typical PC to an embedded system. We
  found such a scale-down in computation based on exemplar processors,
  e.g., Intel's i7 quad-core vs ARMv8 dual-core.}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
that can run about 30fps on a low-end hardware. In this direction, we used HoG and
color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
the first convolutional layer features lead to slightly better precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
features to get the response map. In the next stage, they use the translation estimation from the first stage to
employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
more representative features of the object. However, such approach requires multiple runs of a KCF at a single
frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
deep learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target information loss.}
\label{fig:Filters_CNN}
\end{figure}

\begin{figure}[t]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems already come with an image acquisition
pipeline, and a tremendous amount of progresses on research has been
made for many areas in computer vision. However, to successfully
deploy a computer vision algorithm on any existing embedded systems, a
vision algorithm needs to satisfy, at least, two criteria with
assumption of reasonably good performance: minimal, manual
intervention after deployment and small footprint of consuming
computational resources and executable code. To develop a single,
target tracking system in high accuracy and run-time performance while
these criteria kept in mind, we propose an ensemble of the kernelized
correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed, run-time performance, we deploy each of KCFs in turn. For
a smooth transition between individual KCFs' executions, we developed
a Bayes filter. Experimental results showed that the performance of
ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. These results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Moreover our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a lightweight or an array of monocular
cameras. Given such a trend, instead of just manually flying for video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-450$ fps, aiming at running, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would not be easy to compare run-time
  performance of a computer vision algorithm at an Intel or AMD
  processor running on a desktop or a laptop and at that, e.g., ARM,
  of a single-board, embedded system. This is primarily due to the
  difference in their architectures and available computing
  resources. To derive these numbers (300 and 30 fps), we assume that
  there is roughly, at least, an 1/10th scale down of computational
  resources from a typical PC to an embedded system. We found such a
  scale-down in computation based on exemplar processors, e.g.,
  Intel's i7 quad-core vs ARMv8 dual-core.}

@@

One of the dominant frameworks for online, object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

\textbf{Deep Learning Features} Our focus so far was to build a high
speed tracker that can run about 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep Learning features, on
the other hand, recently have been proved to boost tracking accuracy
of some of the online tracking algorthms \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep learning features if
a target embedded system has GPUs.

{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

  I don't know why Figure 6 is presented separately from Figure 5. If
  you want to keep this way, you need, at least, to have their scales
  same -- precision should have the same range, say 0.8 as the max
  value.

  It seems most of reference on DNN hasn't added to the .bib file yet.
}

For example, \cite{danelljan2015convolutional} used the activations of
the first and second convolutional layer features of the VGGNet
\cite{simonyan2014very} where their experiments showed that the first
convolutional layer features lead to slightly better precision and
success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to get the response map. In the
next stage, they use the translation estimation from the first stage
to employ second convolutional layer features. Finally, the first
convolutional layer features is extracted from the position estimated
in the second stage. This coarse-to-fine position estimation approach
allows embedding more representative features of the object. However,
such approach requires multiple runs of a KCF at a single frame,
increasing the run-time complexity. For this reason, we follow a
similar approach to \cite{danelljan2015convolutional} to embed deep
learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different
feature  representations.  The  translation filters,  $R_{t}^{L}$  and
$R_{t}^{S}$,   considers  at   more  than   twice  larger   area  than
$R_{s}$.  Taking  this into  account,  we  can assign  deeper  feature
encodings  to $R_{s}$  as it  requires less  spatial information  than
$R_{t}^{L}$ and $R_{t}^{S}$.  Hence, we assign the  activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$  and $R_{t}^{S}$  are assigned the  activations of
the  second  layer  features  ($109\times109\times64$).  This  feature
assignment  is represented  as \textit{conv224-VGG}.  Additionally, we
assign  the  second convolutional  layer  features  to $R_{s}$  as  in
$R_{t}^{L}$    and    $R_{t}^{S}$    and    compare    this    setting
(\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the  VGGNet as
it provides  higher spatial resolution  at the first layers  than than
AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[h]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
